---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# teleporrrt

<!-- badges: start -->
<!-- badges: end -->

The goal of teleporrrt is to construct detailed visuals and analyze different features of the
*Teleport API*

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DeclanMolony/teleporrrt")
```
```{r}
library(teleporrrt)
```


## Cities in the Teleport API

You can use the function `city_lookup()` to produce a dataframe of all the cities used in the Teleport API, and their html links.

```{r}

#city_lookup()
```


## Individual City Links

You can use the function `city_link()` to produce an html link for a particular city's scores to be used for your own analysis:

```{r}
city_link("Dublin")
```


## Dataframes

You can create a dataframe of a single city's Teleport metrics:

```{r}
city_dataframe("New York")
```

Or create a dataframe comparing two cities:

```{r}
city_combine_df("Cairo","Zurich")
```

Or create a dataframe with the closest City to a given Longitude/Latitude coordinates

```{r nearest_city}
#Coordinates of the White House
nearest_city(lat = 38.8977, lon = -77.0365)
```


## Spider Chart

You can even create a radar/spider chart comparing two cities' scores

```{r, fig.width=10, fig.height=10}
city_radarchart("Hong Kong","Detroit")
```


## City Ratings

You can input a list of cities you're interested in comparing based on cost of living, housing, or education, and find out which of the cities has the maximum rating and which has the minimum rating

```{r}
MaxMinRating(c("Toronto", "Vancouver"), "Cost of Living")
```



